\chapter{Acknowledgements}

First and foremost, I would like to express my deepest gratitude to my supervisor, Nicolas Sangouard, who, four years ago, gave me the opportunity to join his group first in Basel, then in Paris.
Nicolas has always been extremely supportive and available, and his many precious advices, both scientific and personal, helped me grow a lot.
I especially appreciate the efforts Nicolas has put in creating a pleasant group environment.
It has been an immense joy to share all of these moments, from la Roche de Solutré to Fontainebleau.
I could not have hoped for a better supervisor, Nicolas, merci du fond du coeur.

\medbreak

I owe big gratitude to Jean-Daniel Bancal, the friendliest co-worker who turned into an amazing co-supervisor. 
I am particularly thankful to Jean-Daniel for our scientific discussions and for his incredible pedagogy.
Jean-Daniel has taught me a lot, his feedback on this thesis has been invaluable, and he makes a fantastic vin de noix.


\medbreak

I am grateful to Eleni Diamanti, Nicolas Brunner, Toni Acín and Peter Brown for accepting to be part of my jury.
I am deeply indebted, in particular, to Nicolas and Toni who have introduced me to the field of quantum information back in my master and who have agreed to review this manuscript.

\medbreak

During my PhD I met many wonderful people. 
In Basel, I had fantastic colleagues in our Quantum Goptnics group: Alexey, Azadeh, Davide, Melvyn and Sebastian, thank you for being amazing colleagues.
I am particularly grateful to Enky Oudot and Pavel Sekatski, who helped me a lot in Basel, both scientifically and personally. 
You guys also taught me how to open a beer with two standing desks.
In Paris, I have been surrounded by incredible people at the Institut de Physique Théorique.
Elie, Juli and Victor many thanks for being amazing office mates, Skype mates, and colleagues.
Juli, our friendship has been a true fortune, from Basel to Paris, in the ups and downs. 
I would gladly exchange more debugging time against your culinary delicacies.
Bastien, Corentin and Pierre, it has been a too short but lovely time, I wish you all a great PhD.
I also want to thank the people who, all in their unique ways, made these last years memorable : Dario, Ernest, Felix, Flavio, Grégoire, Jed, Joe and Gaby, Marc-Oliver and Peter.


\medbreak

Supports from outside the field has been incredibly precious, and a paragraph would never be sufficient to express my gratitude.
I received so much love from my friends of the CFFH and RadioMambo, thank you a thousand.
Coline, Eliso, Jéri, Legzouz and his chat, Matt, Maxence and Will, time with you has been always priceless and revitalizing.
A particular thanks goes to Dodo that not only has been a true friend but has also produced a beautiful artwork for this thesis.
Max and Livia, danke viel viel mol. 
Diego, my crimpy lobster, I cherish our friendship so much, you have been an essential support through these years.
To my bouldering friends from Elys and elsewhere, thank you for all the fun and the beta.
Shanta, Sofie, Sobi and all my Kleibasel peeps, I owe you.

\medbreak


À ma famille, pépère, maman et papa, un énorme merci pour votre soutien, votre générosité et votre amour inconditionnel, je vous dois tant.
Maxime et Chloé, merci mille fois pour tous ces moments à Paris, votre accueil, et votre confortable canapé-lit.

\medbreak

Märta, nothing that I could ever write will be grateful enough.
Your love, support and understanding has been boundless, even when I didn't wake up to make your coffee.
I am looking forward to go on the next adventure with you.

