\chapter{Publications}

This thesis is based on the following contributions.

\paragraph{Publications:}
\begin{enumerate}
	\item 
		\textit{What is the minimum CHSH score certifying that a state resembles the singlet?} \\
		Xavier Valcarce, Pavel Sekatski, Davide Orsucci, Enky Oudot, Jean-Daniel Bancal, and Nicolas Sangouard. \\
		\textit{Quantum}, volume 4, page 246.
	\item 
		\textit{Self-testing two-qubit maximally entangled states from generalized Clauser-Horne-Shimony-Holt tests} \\
		Xavier Valcarce, Julian Zivy, Nicolas Sangouard, and Pavel Sekatski. \\
		\textit{Phys. Rev. Research} 4, 013049.
	\item
		\textit{Device-independent quantum key distribution from generalized CHSH inequalities} \\
		Pavel Sekatski, Jean-Daniel Bancal, Xavier Valcarce, Ernest Y.-Z. Tan, Renato Renner, and Nicolas Sangouard. \\
		\textit{Quantum}, volume 5, page 444.
	\item 
		\textit{Automated design of quantum optical experiments for device-independent quantum key distribution}  \\
		Xavier Valcarce, Pavel Sekatski, Elie Gouzien, Alexey Melnikov, Nicolas Sangouard. \\
		\textit{Phys. Rev. A} 107, 062607.
\end{enumerate}

\paragraph{Codes:}
\begin{enumerate}
	\setcounter{enumi}{4}
	\item \textsc{QuantumOpticalCircuits.jl} --- Julia framework for the simulation of photonic circuits. \\
		\url{https://github.com/xvalcarce/QuantumOpticalCircuits.jl}
	\item \textsc{SPDCStats.jl} --- Julia package to compute statistics arising from a SPDC source and non photon-number resolving photodetectors. \\
		\url{https://github.com/xvalcarce/SPDCStats.jl}
\end{enumerate}
